---
title: "Developing Data Product - Week 4 Assignment"
author: "Sarang Pande"
date: "17 April 2019"
output: ioslides_presentation
---

## Coursera Reproducible Pitch

This is a task for the data science coursera course about developing data products for week 4. As part of this, I have created a shiny app and deployed it on the shiny server. The link is https://srng.shinyapps.io/shinyApp/. The code can be found at 

## Overview

The shiny app plots graph against miles per gallon (mpg) for different variables from the mtcars dataset.

```{r }
head(mtcars)
```

## UI Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)

shinyUI(fluidPage(
  
  # Application title
  titlePanel("Cars Dataset - Miles per Gallon"),
  
  sidebarPanel(
    
    selectInput("variable", "Variable:", 
                c("Cylinders" = "cyl",
                  "Transmission" = "am",
                  "Gears" = "gear"))
  ),
  
  mainPanel(
    # Output: Formatted text for caption ----
    h3(textOutput("caption")),
    
    # Output: Plot of the requested variable against mpg ----
    plotOutput("mpgPlot")
  )
))
```

## Server Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(plotly)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg vs ", input$variable)
  })
  
  output$caption <- renderText({
    formulaText()
  })

  output$mpgPlot <- renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})
```

